---
title: "Final Presentation"
author: "Author: Sally Campbell"
date: "`r format(Sys.time(), '%B %d, %Y @ %I:%M %p')`"
output: ioslides_presentation
---

```{r global_options, include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  comment = NA
)
```

## Packages Used

I used tidyverse for data manipulation and plotting.

```{r, echo = TRUE}
library(tidyverse)
```


## Biodiversity in National Parks Dataset



**Variables in the Dataset:** 

**Parks**

* `Park Code`: park identification code

* `Park Name`: name of park

* `State`: state of park

* `Acres`: acres of park

* `Latitude` & `Longitude`: latitude and longitude of park


## Biodiversity in National Parks Dataset

**Species**

* `Species ID`: species identification code

* `Park Name`: location of species

* `Category`, `Order`, `Family`: taxonomic information

* `Scientific Name`: scientific name

* `Common Names`: one or more common names

* `Record Status`: record status

## Biodiversity in National Parks Dataset

**Species**

* `Occurence`: verification of species presence in park

* `Nativeness`: species native or foreign to park

* `Abundance`: presence and visibility of species in park

* `Seasonality`: season and nature of presence in park

* `Conservation Status`: species classification according to US Fish & Wildlife Service








```{r}
parks <- read_csv("data/parks.csv") 
species <- read_csv("data/species.csv")
```

##

```{r, fig.align = "top", fig.width = 8.5, fig.height=6.3}
nns <- species %>% 
  full_join(parks,by="Park Name") %>%
  filter(Nativeness == "Not Native" | Nativeness == "Native") %>%
  ggplot(aes(y =(reorder(`Park Name`, desc(`Park Name`))), color= Nativeness, fill=Nativeness)) +
  geom_bar(position="fill", size=.75, color="white") +
  scale_x_continuous(labels = scales::percent) +
  theme_minimal() +
  labs(
    title = "Percentage of native vs non-native species by park",
    x = "Percentage of species",
    y = "Parks"
  )

nns + scale_fill_manual(values = c("Native" = "#ADDFF9",
                                "Not Native" = "#FFAB80")) + theme(axis.text.y = element_text(size = 8))   
```

##

```{r, fig.align = "center", fig.width = 8.5, fig.height=6.3}
es <- species %>% 
  full_join(parks,by="Park Name") %>%
  filter(`Conservation Status` == "Endangered" | `Conservation Status` == "In Recovery", State == "AK" | State == "CA" | State == "CO" | State == "HI" | State == "MT" | State == "NV" | State == "OR" | State == "UT" | State == "WA" | State == "WY") %>%
  ggplot(aes(color=`Conservation Status`, x=State, fill=`Conservation Status`)) +
  geom_bar(size=.5) +
  scale_y_continuous(
    breaks = seq(from = 0, to = 100, by = 10)) +
  theme_linedraw()+
  labs(
    title = "Endangered vs in recovery species by state in the Western Region",
    subtitle = "*Not including data from Death Valley National Park or Yellowstone National Park",
    x = "States",
    y = "Count"
  )

 es + scale_fill_manual(values = c("Endangered" = "#ADDFF9",
                                "In Recovery" = "#EA8F9E")) + scale_color_manual(values = c("Endangered" = "#ADDFF9",
                                "In Recovery" = "#EA8F9E"))

```

